\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   The contracting of software is a common practice within the Brazilian Public Departments. At the moment the company wins the bid for a service, the company will have the right to contract, to render the service to the contracting entity. This work aims to implement a dashboard that, with the help of visual resources, is a tool that helps in the process of contracting software in Public Departments. For this solution, the dashboard works as a tool for visualizing indicators, as determined by the Public Department Project Manager. The dashboard displays the project indicators, which are being developed by the Employer, for the Manager. The work consisted of two phases: Initiation and Execution. The objective of the first phase is to establish fundamentals (theoretical and architectural) for the Execution phase, while the focus of the second phase lies in the implementation of the solution. The use of an adaptation of the Scrum methodology for the development of the solution was chosen, but some changes were necessary, mainly due to the scope and number of roles required by the methodology. Machine Learning was used in suggesting possible metrics for managers, based on the profiles of other managers. In this case people were created to represent these profiles.

   \vspace{\onelineskip}
 
   \noindent 
   \textbf{Key-words}: dashboard. quality. hiring software. monitoring metrics. indicators. Machine Learning. Personas
 \end{otherlanguage*}
\end{resumo}
